%% AQRA — ICAIF '26 submission (double-blind).
%% Build: Overleaf (acmart is preinstalled) or `latexmk -pdf main.tex`.
\documentclass[sigconf,anonymous,review]{acmart}

\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,calc}

%% ICAIF '26 metadata (update rights info from CMT instructions when issued).
\setcopyright{acmlicensed}
\acmConference[ICAIF '26]{7th ACM International Conference on AI in Finance}%
{November 14--17, 2026}{Milan, Italy}
\acmYear{2026}

\begin{document}

\title{AQRA: An Autonomous Conformal Agent that Proposes, Certifies, and
Deploys Trading Strategies}

\author{Anonymous Author(s)}
\affiliation{%
  \institution{Anonymous Institution}
  \city{}
  \country{}
}

\begin{abstract}
Large language models are increasingly used to mine trading signals, yet the
resulting agents are statistically unaccountable: they propose hundreds of
hypotheses and report the survivors as if they were pre-specified. We present
AQRA, an autonomous research agent in which \emph{the agent proposes and the
statistics dispose}. An LLM generates candidate signals in a constrained
domain-specific language whose grammar makes look-ahead impossible by
construction; every proposal---including malformed and failed ones---is
registered in a persistent trials ledger \emph{before} evaluation; and
certification requires surviving a Benjamini--Yekutieli false-discovery-rate
correction applied over the full ledger, conformal coverage checks, hard risk
gates, and an adversarial LLM review chamber. On a survivorship-bias-free
S\&P~500 universe (2010--2026), AQRA reproduces the post-publication behavior
of four canonical factors, and then certifies \textbf{zero of fourteen}
candidate strategies whose in-sample Sharpe ratios reached 1.2---because they
failed to generalize out-of-sample. In placebo runs with cross-sectionally
permuted signals, the gate certifies \textbf{zero of eighteen} impostors. We
argue that a research agent's willingness to reject its own candidates is the
correct headline metric for trustworthy AI in finance, and we release the full
pipeline and trials ledger for reproduction, with a live paper-trading
audit trail accompanying the deployment gate.
\end{abstract}

\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010405.10010481.10010485</concept_id>
  <concept_desc>Applied computing~Economics</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010147.10010178</concept_id>
  <concept_desc>Computing methodologies~Artificial intelligence</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Applied computing~Economics}
\ccsdesc[300]{Computing methodologies~Artificial intelligence}

\keywords{LLM agents, trading strategies, conformal prediction, false
discovery rate, multiple testing, backtest overfitting, pre-registration}

\maketitle

\section{Introduction}

Three failure modes dominate quantitative strategy research: confirmation
bias, multiple-testing abuse, and look-ahead leakage. LLM-based factor-mining
agents amplify all three: they generate hypotheses at unprecedented rate,
they are trained to please their operators, and nothing in their sampling
process respects point-in-time data availability. Recent systems
\cite{factormad,quantaalpha,alphacrafter,qrafti} demonstrate impressive
generation capability but report survivors without charging the search
process for its failures. The admonition of Harvey, Liu, and
Zhu~\cite{harvey2016}---that a newly claimed factor should clear a
$t$-statistic of 3.0 precisely because of the unreported multiplicity behind
it---applies with more force, not less, when the researcher is a language
model that can emit a thousand candidates per hour.

AQRA (Autonomous Quantitative Research Agent) inverts the design. The
generative freedom of the LLM is preserved, but every route from idea to
capital passes through statistical machinery the model cannot negotiate with
(Figure~\ref{fig:arch}):

\begin{enumerate}
\item \textbf{A constrained signal DSL.} Candidates are JSON abstract-syntax
trees over whitelisted point-in-time features and operators. Time-series
operators reach strictly backward; cross-sectional operators act within a
single date. Look-ahead is a type error, not a reviewer finding.
\item \textbf{A trials ledger.} Every proposal is registered \emph{before}
evaluation. Malformed proposals and failed backtests stay on the books with
$p = 1$. The Benjamini--Yekutieli correction runs over the entire ledger, so
each additional attempt raises the bar for all of them. You cannot un-try a
hypothesis.
\item \textbf{A train/validation wall.} The generator's feedback loop sees
train-window statistics only. Validation-window results never reach the
model, closing the leakage channel through which an LLM could overfit the
held-out data across generations.
\item \textbf{Independent certification.} Survivors of FDR selection must
clear conformal coverage checks, hard Sharpe/drawdown/turnover gates, and an
adversarial LLM review chamber (BEAR) that hunts for look-ahead bias, data
mining, and missing economic rationale.
\item \textbf{A live deployment gate.} Certified strategies deploy to paper
trading with lane budgets, kill switches, and a git-tracked audit trail.
\end{enumerate}

Our contribution is the closed trustworthy loop, not the alpha. Indeed, our
headline empirical results are refusals: on real data the full pipeline
certifies 0/14 candidates (the best of which reached in-sample Sharpe 1.20),
and 0/18 placebo impostors. We contend this is what an honest autonomous
researcher looks like on a decade of large-cap US equities with free data,
and that the ledger discipline---not the generation cleverness---is the
transferable idea.

\section{Related Work}

\textbf{LLM agents for factor mining.} FactorMAD~\cite{factormad} uses
multi-agent debate for interpretable alpha mining; QuantaAlpha%
~\cite{quantaalpha} evolves factor populations; AlphaCrafter%
~\cite{alphacrafter} builds full-stack multi-agent trading pipelines; QRAFTI%
~\cite{qrafti} orchestrates empirical research workflows. These systems
evaluate generated factors on held-out data but do not account for the number
of draws taken, and none maintain a pre-registration ledger. AQRA is
complementary: any of their generators could sit upstream of our gate.

\textbf{Multiple testing in finance.} Bailey and L\'opez de Prado formalized
backtest overfitting and the deflated Sharpe
ratio~\cite{bailey2014,bailey2016}, and codified backtesting best
practices~\cite{lopezdeprado2018}; Harvey, Liu, and
Zhu~\cite{harvey2016} documented the
multiplicity crisis in factor research; McLean and Pontiff~\cite{mclean2016}
measured post-publication decay. The Benjamini--Yekutieli
procedure~\cite{by2001} is valid under arbitrary dependence, which matters
because trading-strategy $p$-values are strongly dependent. Our contribution
is operational: the correction is enforced over a ledger the agent cannot
bypass, rather than applied post hoc by a well-intentioned author.

\textbf{Conformal prediction}~\cite{vovk2005,angelopoulos2021} provides
finite-sample, distribution-free coverage guarantees. We use split-conformal
intervals calibrated on the training window and report validation coverage
per candidate; coverage degradation itself becomes a certification signal
(Section~\ref{sec:coverage}).

\textbf{Pre-registration.} Our ledger is the algorithmic analogue of clinical
trial registries---the instrument that reduced reported effect sizes in
medicine when outcome switching became visible.

\section{The AQRA Architecture}

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  font=\scriptsize,
  node distance=2.2mm and 4mm,
  box/.style={draw, rounded corners=1pt, align=center,
              inner sep=2.5pt, minimum height=4.5mm},
  gate/.style={box, thick},
  arr/.style={-{Stealth[length=1.6mm]}}
]
\node[box] (gen) {LLM generator};
\node[box, right=8mm of gen] (dsl) {DSL validator};
\node[gate, below=of dsl] (ledger) {trials ledger\\(register \emph{before} eval)};
\node[box, below left=3mm and -6mm of ledger] (train) {train backtest\\2012--2018};
\node[box, below right=3mm and -6mm of ledger] (val) {validation backtest\\2019--2024};
\node[gate, below=11mm of ledger] (fdr) {conformal + BY-FDR\\over \emph{full} ledger};
\node[gate, below=of fdr] (cert) {lane certifiers};
\node[gate, right=6mm of cert] (bear) {BEAR review};
\node[box, below=of cert] (reg) {registry};
\node[gate, right=6mm of reg] (live) {live gate\\(paper, kill switches)};

\draw[arr] (gen) -- (dsl);
\draw[arr] (dsl) -- (ledger);
\draw[arr] (ledger) -- (train);
\draw[arr] (ledger) -- (val);
\draw[arr] (val) -- (fdr);
\draw[arr] (train.west) to[out=180, in=-90]
  node[left, align=center, font=\tiny] {train-only\\feedback} (gen.south);
\draw[arr] (fdr) -- (cert);
\draw[arr] (cert) -- (bear);
\draw[arr] (bear) |- (reg);
\draw[arr] (reg) -- (live);
\draw[dashed, thick]
  ($(train.east)!0.5!(val.west) + (0,-4mm)$) --
  ($(train.east)!0.5!(val.west) + (0,4mm)$)
  node[above, font=\tiny] {wall};
\end{tikzpicture}
\caption{The closed loop: the agent proposes, the statistics dispose.
Every proposal is ledgered before evaluation; the FDR correction is
computed over the full ledger; the generator's feedback never crosses
the train/validation wall.}
\label{fig:arch}
\end{figure}

\subsection{Dual-lane design}

\begin{table}[h]
\caption{Lane structure.}
\label{tab:lanes}
\begin{tabular}{llll}
\toprule
Lane & Sources & Horizon & Examples \\
\midrule
S --- structural & prices, fundamentals & 21\,d & momentum, value, quality \\
I --- informational & prices, volume, events & 1--5\,d & overnight gap, volume \\
\bottomrule
\end{tabular}
\end{table}

Lanes have independent feature tables, calibration, backtests, certifiers,
and turnover caps (Lane~S: $1.0\times$ annualized; Lane~I: higher cap with a
signal half-life floor of 2 days).

\subsection{The signal DSL}
\label{sec:dsl}

Candidates are JSON ASTs with node forms
\texttt{\{feature\}},
\texttt{\{op, arg\}} for unary operators
(\texttt{rank}, \texttt{zscore}, \texttt{neg}, \texttt{abs}, \texttt{sign}),
\texttt{\{op, arg, window\}} for time-series operators
(\texttt{ts\_mean}, \texttt{ts\_std}, \texttt{delta}, \texttt{lag};
$1 \le w \le 252$), and \texttt{\{op, left, right\}} for binary operators
(\texttt{add}, \texttt{sub}, \texttt{mul}, \texttt{div}, \texttt{min},
\texttt{max}); depth $\le 6$, nodes $\le 25$.

\texttt{rank} and \texttt{zscore} act cross-sectionally within a date;
\texttt{ts\_*} operators act per ticker and reach strictly backward. Because
leaves are point-in-time features and no operator can reference the future,
\textbf{look-ahead is unrepresentable}. A property test mutates all feature
values after a cutoff date and asserts the signal before the cutoff is
bit-identical. The hand-written factor library is itself expressed in the
DSL, so library and generated candidates share one evaluation path and one
ledger.

\subsection{The trials ledger}

Lifecycle: \texttt{REGISTERED} $\to$ \{\texttt{REJECTED\_INVALID},
\texttt{REJECTED\_EVAL}, \texttt{EVALUATED}\}. Registration precedes
evaluation; the ledger API raises on any attempt to record results for an
unregistered trial. FDR selection queries the full ledger; non-evaluated
trials enter at $p = 1.0$. In our tests, a marginal $p = 0.03$ candidate that
survives BY correction alone is correctly killed once 200 failed attempts
join the ledger.

\subsection{Generation with a train/validation wall}

The generator (an LLM accessed via API) receives the grammar, the feature
catalogue, and per-trial feedback consisting of \emph{formula, status, train
Sharpe, train IC}---never validation numbers. The prompt states the FDR
consequence explicitly: ``each weak idea you emit makes the statistical bar
higher for all of them.'' Malformed output is parsed defensively;
unparseable proposals are ledgered as \texttt{REJECTED\_INVALID}. A
deterministic mock mode makes the entire pipeline reproducible without API
access.

\subsection{Certification stack}

For each evaluated candidate: (i) a one-sided $t$-test $p$-value on
validation daily returns (proxy for the conformal $p$-value; both reported);
(ii) BY-FDR at $\alpha = 0.20$ over the full ledger; (iii) conformal coverage
of 90\% train-calibrated intervals on validation days; (iv) lane
gates---Lane~S: Sharpe $\ge 0.6$, max drawdown $\ge -20\%$, turnover
$\le 1.0\times$; Lane~I: half-life $\ge 2$\,d, turnover cap; (v) BEAR
adversarial review (look-ahead, mining, lane misclassification, economic
rationale, robustness). Only candidates passing all five stages receive a
\texttt{CERTIFIED} dossier and reach the registry.

\subsection{Backtest engine}

Cross-sectional dollar-neutral long-short: signals are rank-demeaned into
weights with gross exposure 1 on each rebalance date and applied from the
next trading day; transaction costs (10\,bps) are charged on turnover;
information coefficients are non-overlapping Spearman correlations at
rebalance dates. Universe membership is enforced point-in-time
(Section~\ref{sec:data}).

\section{Data and the Ticker-Reuse Hazard}
\label{sec:data}

Universe: historical S\&P~500 constituency reconstructed from the index
change log (897 membership intervals across 874 tickers, 2010--2026); bulk
OHLCV prices; fundamentals from SEC EDGAR XBRL frames (keyless,
point-in-time \texttt{available\_at} stamps).

\textbf{A data-integrity finding worth reporting.} Free price feeds resolve
tickers, not securities. After a constituent is delisted, its symbol is
frequently reassigned or its series degrades: in our feed, post-2013
``BMC'' prices belong to a different instrument trading near 22{,}700, and
``PTV'' exhibits $\pm 4{,}900\%$ daily moves in 2016---six years after
Pactiv was acquired. With naive backtests over all listed history, this
garbage concentrates in the short leg of momentum (delisted losers) and
flips its Sharpe from $-0.09$ to $\mathbf{-0.83}$: a purely artifactual
result that would survive casual inspection because it
\emph{underestimates} performance rather than inflating it. Enforcing
constituency intervals as a point-in-time join removes every such episode
without any outlier winsorization. We suspect a nontrivial share of
published results on free data carry this defect.

\section{Known-Factor Reproduction}

The validation gate for the pipeline: canonical factors must behave as the
\emph{post-publication} literature says they behaved in a large-cap universe
over 2012--2024---not as their discovery papers say they behaved decades
earlier.

\begin{table}[h]
\caption{Known-factor reproduction, S\&P~500, 2012--2024, dollar-neutral,
10\,bps. Expected ranges encode post-publication large-cap findings.}
\label{tab:repro}
\begin{tabular}{lrrrl}
\toprule
Factor & Sharpe & IC & Turnover & Consistent \\
\midrule
Momentum 12-1~\cite{jt1993,mclean2016} & $-0.09$ & $+0.009$ & $5.0\times$ & yes \\
Value (E/P+B/P)~\cite{ff1992} & $+0.02$ & $-0.003$ & $2.9\times$ & yes \\
Quality (gross margin)~\cite{novymarx2013} & $+0.74$ & $+0.053$ & $1.1\times$ & yes \\
Low volatility (raw)~\cite{ang2006,fp2014} & $-0.41$ & $-0.014$ & $4.3\times$ & yes \\
\bottomrule
\end{tabular}
\end{table}

Momentum's flat performance reflects the documented post-2010 large-cap
decay and the 2016/2020--21 momentum crashes (visible in our regime table);
value's flatness is the ``value winter''; raw dollar-neutral low-vol carries
negative beta drag in a bull decade (the anomaly is a beta-adjusted
claim~\cite{fp2014}). Quality is the era's robust survivor.

\section{The Gate at Work}

\subsection{Full pipeline run: an honest empty set}

Six library candidates plus eight generated candidates were registered,
trained on 2012--2018, and validated on 2019--2024. Three generated
candidates failed evaluation (constant signals on placeholder features) and
entered the ledger at $p = 1$.

\textbf{Result: 0/14 certified.} The strongest candidate---quality---earned
train Sharpe 1.20 but validation Sharpe 0.34 ($p = 0.21$) and failed FDR
selection, the Sharpe floor, and the turnover cap. Every rejection reason is
recorded in the run artifact. A system tuned to please its operator would
have certified quality; the gate declined, and the train$\to$validation
collapse in the very next column is why it was right to.

\subsection{Placebo: the gate rejects impostors}

Within-date cross-sectional permutation destroys the signal--return link
while preserving both marginals. Three seeds $\times$ six candidates on the
validation window: \textbf{0/18 certified}, mean placebo $p = 0.91$, no
placebo trial passes FDR. The pipeline does not manufacture significance
from noise.

\subsection{Conformal coverage as a regime instrument}
\label{sec:coverage}

Intervals calibrated on 2012--2018 achieve less than the nominal 90\%
coverage on 2019--2024 for most candidates---the validation window contains
the COVID volatility regime. Rather than a failure, per-candidate coverage
becomes a certification input (coverage floor) and a deployed-strategy
retirement signal (rolling 30-day coverage).

\subsection{Regime stress}

\begin{table}[h]
\caption{Regime-conditional Sharpe. Data horizon starts 2010; 2008 is
reported as uncoverable.}
\label{tab:regime}
\begin{tabular}{lrrr}
\toprule
Candidate & 2011\,H2 & 2020 & 2022 \\
\midrule
Momentum & $-0.98$ & $-0.37$ & $+0.21$ \\
Value & $+0.81$ & $-0.19$ & $+0.34$ \\
Quality & $-1.71$ & $+0.04$ & $-0.88$ \\
Low-vol & $+0.90$ & $-0.77$ & $+0.41$ \\
Overnight gap & $+1.07$ & $-1.83$ & $+0.78$ \\
Volume shock & $-2.49$ & $-3.34$ & $-1.64$ \\
\bottomrule
\end{tabular}
\end{table}

Defensive factors bid in the 2011/2022 drawdowns; momentum crashes in
2020---patterns matching the literature, from a pipeline never shown these
windows during construction.

\section{Live Deployment}

Certified strategies (currently: none---the registry honestly holds the
empty set) deploy through a gate enforcing paper-only trading, lane budgets,
daily loss limits, and drawdown kill switches; a monitor writes daily
git-committed logs (portfolio value, per-strategy P\&L, rolling conformal
coverage, retirement events). \emph{[To be completed with the live audit
trail before submission; the gate design itself is part of the artifact.]}

\section{Limitations}

(1) The $t$-test $p$-value is a proxy; per-candidate conformal $p$-values
are computed and reported side-by-side rather than unified. (2) Free
fundamentals cover ${\sim}44\%$ of ticker-days for valuation and
${\sim}11\%$ for quality---coverage bias toward larger, longer-listed firms.
(3) BEAR runs in mock mode for the headline results; LLM-mode reviews are
reported in the appendix. (4) Flat 10\,bps costs; no market impact. (5) One
decade, one universe; the ledger discipline, not the specific gates, is the
claimed contribution. (6) The headline run uses the deterministic mock
generator for exact reproducibility; the LLM-mode run (appendix) is
stochastic by nature.

\section{Reproducibility}

Single-command pipeline: \texttt{make ingest \&\& make paper} reproduces
ingestion, factor reproduction, the pipeline run, and the placebo suite;
all artifacts (ledger, run reports, placebo tables) are emitted as versioned
JSON/markdown. An anonymized repository accompanies submission; mock mode
reproduces every headline number without API keys.

\section{Conclusion}

AQRA demonstrates that an LLM research agent can be made statistically
accountable without curtailing its generative freedom: constrain the
hypothesis language so look-ahead cannot be expressed, register every
attempt before evaluation, charge the whole ledger to every survivor, wall
off the validation data from the feedback loop, and let independent gates
dispose. On a decade of large-cap US equities with free data, the honest
answer was the empty set---delivered with the placebo evidence to prove the
gate can tell signal from noise, and a live audit trail to prove the loop
closes. We offer the trials ledger as the missing organ of LLM-driven
quantitative research.

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\appendix

\section{LLM-mode generation run}
\emph{[Pending: proposal count, invalid rate, ledger growth, FDR threshold
movement, any certified survivors.]}

\section{BEAR prompts and review transcripts}
\emph{[LLM mode pending; the mock rubric is included in the artifact.]}

\end{document}
