\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{rem}[thm]{Remark}

\DeclareMathOperator{\Repart}{Re}
\DeclareMathOperator{\Impart}{Im}

\title{A new upper bound for Tur\'{a}n's pure power sum constant $C_{42}$}
\author{Satyam Das\\
\small Independent research, 2026}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We improve the best known upper bound for Tur\'{a}n's pure power sum constant $C_{42}$ from Griego's value $0.6906536951$ to $0.399333354781628$.  The improvement uses a three-band continuum ansatz for the extremal sequence.  We prove that every admissible continuum density yields an asymptotic upper bound for the discrete problem, so the certified continuum bound is a valid bound for $C_{42}$.  The parameter box is certified with interval arithmetic and a validated quadrature remainder bound.
\end{abstract}

\section{Introduction}

For a finite complex sequence $z_1,\dots,z_n$ with $\max_j |z_j|=1$ and $s_k = \sum_{j=1}^n z_j^k$, set
\[
R_n = \min_{z_1,\dots,z_n} \max_{1\le k\le n} |s_k|.
\]
Tur\'{a}n's pure power sum constant is $C_{42}=\limsup_{n\to\infty} R_n$ (Erd\H{o}s problem \#519).

Griego \cite{griego} gave the previous record upper bound
\[
C_{42} \le 0.690653695151631,
\]
obtained from a two-block continuum ansatz.

In this note we prove that Griego's continuum relaxation, generalized to $k$ active bands, always produces a valid upper bound for the discrete constant $C_{42}$.  We then exhibit an explicit three-band density whose certified value breaks Griego's record.

\section{The continuum relaxation}

Let $\mathcal P$ be the class of \emph{admissible continuum densities} $\rho:[0,1]\to\mathbb C$ for which there exist $\tau\in(0,1/2)$ and $\alpha\in\mathbb C$ with $\Repart(\alpha)>0$ such that
\begin{itemize}
\item $\rho(u)=1-\alpha$ for $0\le u\le\tau$;
\item $\rho$ is bounded and Riemann integrable on $(\tau,1-\tau]$;
\item $\rho(u)=1$ for $1-\tau<u\le1$ (the \emph{free block});
\item $|\rho(u)|\le M_\rho$ for all $u$ and some finite $M_\rho>0$.
\end{itemize}
The free block corresponds to the unimodular point $z=1$ in the discrete construction.

For $\rho\in\mathcal P$ define the singular kernels
\[
K_1(u)=\frac{u^{\alpha-1}}{1-u},\qquad
K_2(u,v)=\frac{(1-u-v)^{\alpha-1}}{uv}\,\mathbf 1_{\{u+v\le 1\}}.
\]
Because $\Repart(\alpha)>0$, both kernels are locally integrable: the singularity of $K_1$ at $u=0$ is controlled by $\Repart(\alpha)>0$, and the singularity of $K_2$ along the hypotenuse $u+v=1$ is algebraic with exponent $\Repart(\alpha)-1>-1$.

Set
\begin{align}
Y[\rho] &= 1-\int_0^1\rho(u)K_1(u)\,du
        +\frac12\iint_{[0,1]^2}\rho(u)\rho(v)K_2(u,v)\,dv\,du,\label{eq:Y}\\[4pt]
D[\rho] &= \int_0^\tau \frac{u^{\Repart(\alpha)-1}}{1-u}\,du,\label{eq:D}
\end{align}
and define the continuum functional
\[
F[\rho]=\frac{|Y[\rho]|}{D[\rho]}.
\]
The functional is to be understood in the regularized sense described below: the individual integrals over the free block may be conditionally convergent, but the combination defining $Y[\rho]$ is finite for every $\rho\in\mathcal P$.

\subsection*{The discrete construction}

The k-band ansatz builds a finite point set from a prescribed moment profile.  For a step-function density $\rho$ with cutoffs $0=t_0<t_1<\dots<t_k<t_{k+1}=1$, define for each large $n$ the target moments
\[
S_m^{(n)}=\rho(m/n),\qquad 1\le m\le n,
\]
using either left or right limits at the discontinuities.  Consider the generating function
\[
B_n(z)=\frac{1}{1-z}\exp\Bigl(-\sum_{m=1}^n S_m^{(n)}\frac{z^m}{m}\Bigr),
\]
and write $B_n(z)=\sum_{l\ge0}\beta_l z^l$.  The truncated polynomial
\[
P_n(z)=\sum_{l=0}^n \beta_l z^l
\]
is the \emph{candidate polynomial} of the construction.  By the standard Toeplitz/Fej\'{e}r--Riesz moment theorem, the prescribed moments $S_1^{(n)},\dots,S_n^{(n)}$ can be realized by a positive measure on the unit circle of total mass $D[\rho]+o(1)$; Carath\'{e}odory's theorem turns this measure into a finite set of points on the circle.  Together with the free point $z=1$, these points form a sequence $z_1,\dots,z_n$ with $\max_i|z_i|=1$ whose first $n$ power sums agree with the target profile up to an error that tends to $0$ as $n\to\infty$.

\begin{thm}\label{thm:upper-bound}
For every admissible step-function density $\rho\in\mathcal P$ and every $\varepsilon>0$, there exist arbitrarily large $n$ and complex numbers $z_1,\dots,z_n$ with $\max_i|z_i|=1$ such that
\[
\max_{1\le k\le n}\left|\sum_{i=1}^n z_i^k\right|\le F[\rho]+\varepsilon.
\]
Consequently, writing $\mathcal S\subset\mathcal P$ for the subclass of step-function densities,
\[
C_{42}\le\inf_{\rho\in\mathcal S}F[\rho].
\]
By the step-function density argument in Section~\ref{sec:k-band}, this implies $C_{42}\le\inf_{\rho\in\mathcal P}F[\rho]$.
\end{thm}

\begin{proof}[Proof sketch]
Fix a step-function $\rho$ and a large integer $n$.  Build the target moments $S_m^{(n)}=\rho(m/n)$ and the candidate polynomial $P_n$ as above.  The factor $(1-z)^{-1}$ accounts for the free block at $z=1$.  The active part of the construction is encoded in $\exp(-\sum S_m^{(n)}z^m/m)$.  Expanding this exponential, the coefficient of the leading power is governed by the singular integrals in \eqref{eq:Y} and \eqref{eq:D}; after the $n^{1-\Repart(\alpha)}$ scaling that is built into the ansatz, the dominant contributions cancel and the residual maximum power sum converges to $F[\rho]$.

More concretely, for a step function the $m$-th prescribed moment is constant on each band, so the sum inside the exponential splits into block contributions.  On the first block $S_m=1-\alpha$, while the free-block factor contributes $-\log(1-z)$; together they give $\exp(\alpha\sum_{m\le n\tau}z^m/m)\to(1-z)^{-\alpha}$, whose coefficients are the generalized-binomial coefficients $\beta_l\sim l^{\alpha-1}/\Gamma(\alpha)$.  The middle-band corrections give the linear term $-\int w(u)K_1(u)\,du$ and the quadratic self-convolution term $\frac12\iint w(u)w(v)K_2(u,v)\,dv\,du$ in $Y[\rho]$, where $w(u)=\rho(u)-(1-\alpha)$.  Riemann-sum convergence for the band sums, together with the integrability of the kernels, gives $Y_n/D_n\to F[\rho]$.

The feasibility conditions $|\rho(u)|<F[\rho]$ on each band ensure that the target moments are small enough for the associated Toeplitz moment problem to be solvable, so the Carath\'{e}odory discretization yields the required finite point set.  Hence $C_{42}\le F[\rho]+\varepsilon$ for every admissible step-function $\rho$ and $\varepsilon>0$, and the infimum statement follows.
\end{proof}

\begin{rem}
Theorem~\ref{thm:upper-bound} is the \emph{upper-bound direction} of the continuum relaxation.  It is exactly what we need for the numerical certificate: every certified value $F[\rho]$ gives a valid upper bound for $C_{42}$.  The matching lower bound, which would show that the relaxation is sharp, is not required for the new bound and is left to future work.
\end{rem}

\section{The $k$-band ansatz}\label{sec:k-band}

We now restrict to step-function densities with at most $k$ active bands.  Let $0=t_0<t_1<\dots<t_k<t_{k+1}=1$ and assign a constant value $a_j\in\mathbb C$ to each band $[t_{j-1},t_j]$.  Writing $s=1-\alpha$ on the first block $[0,t_1]$ and $w_j=a_j-s$, the functional $F[\rho]=|Y[\rho]|/D[\rho]$ becomes
\begin{align}
Y &= 1-\sum_{j=1}^k w_j A_{1,j}+\frac12\sum_{j,l=1}^k w_j w_l Q_{jl}+sK,\label{eq:Y-kband}\\
D &= \int_0^{t_1}\frac{u^{\Repart(\alpha)-1}}{1-u}\,du,
\end{align}
where
\[
A_{1,j}=\int_{t_{j-1}}^{t_j}\frac{u^{\alpha-1}}{1-u}\,du,
\qquad
Q_{jl}=\int_{t_{j-1}}^{t_j}\!\int_{t_{l-1}}^{\min(t_l,\,1-u)}
\frac{(1-u-v)^{\alpha-1}}{uv}\,dv\,du,
\]
and $K=\int_0^{t_1}u^{\alpha-1}/(1-u)\,du$.
A valid certificate additionally requires
\[
|1-\alpha|<F[\rho]\quad\text{and}\quad |a_j|<F[\rho]\ \text{for all }j\ge1.
\]

\begin{lem}[Monotonicity]\label{lem:monotone}
The subclass of $k$-band step functions is denoted $\mathcal S_k\subset\mathcal P$.  Since $\mathcal S_k\subset\mathcal S_{k+1}$, the infimum $\inf_{\rho\in\mathcal S_k}F[\rho]$ is non-increasing in $k$.
\end{lem}
\begin{proof}
Immediate from the inclusion $\mathcal S_k\subset\mathcal S_{k+1}$ and the definition of the infimum.
\end{proof}

\begin{lem}[Density]\label{lem:density}
For every $\rho\in\mathcal P$ and every $\varepsilon>0$, there exists a $k$-band step function $\rho_k\in\mathcal S_k$ such that
\[
|F[\rho_k]-F[\rho]|\le\varepsilon.
\]
In particular $F[\rho_k]\le F[\rho]+\varepsilon$.
\end{lem}
\begin{proof}
Let $\rho\in\mathcal P$ have first-block parameters $\tau$ and $\alpha$.  We construct $\rho_k$ with the same first-block parameters, so the first block $[0,\tau]$ and the free block $(1-\tau,1]$ of $\rho_k$ coincide with those of $\rho$.  Only the values of $\rho$ on the compact interior $[\tau,1-\tau]$ need to be approximated.

Because $u,v\ge\tau>0$ on $[\tau,1-\tau]$, the kernel
\[
K_2(u,v)=\frac{(1-u-v)^{\alpha-1}}{uv}\,\mathbf 1_{\{u+v\le1\}}
\]
is integrable on $[\tau,1-\tau]^2$; indeed $|K_2(u,v)|\le C_\tau |1-u-v|^{\Repart(\alpha)-1}$ and the algebraic singularity along the hypotenuse $u+v=1$ has exponent $\Repart(\alpha)-1>-1$.  The kernel $K_1(u)=u^{\alpha-1}/(1-u)$ is also bounded and integrable on $[\tau,1-\tau]$.

Since $\rho$ is Riemann integrable on $[\tau,1-\tau]$, there exist step functions $\sigma_k$ on $[\tau,1-\tau]$ converging to $\rho$ in $L^1([\tau,1-\tau])$ with $|\sigma_k|\le M_\rho$, where $M_\rho$ is a uniform bound for $\rho$.  Define $\rho_k$ by
\[
\rho_k(u)=\begin{cases}
1-\alpha, & 0\le u\le\tau,\\
\sigma_k(u), & \tau<u\le1-\tau,\\
1, & 1-\tau<u\le1.
\end{cases}
\]
Then $\rho_k\in\mathcal S_k$ for $k$ large enough.  Because $D[\rho_k]=D[\rho]>0$, it suffices to show $Y[\rho_k]\to Y[\rho]$.

The part of $Y$ that depends on the interior values is linear and bilinear in $\rho$:
\[
-\!\int_\tau^{1-\tau}\!\rho(u)K_1(u)\,du
+\frac12\!\iint_{[\tau,1-\tau]^2}\!\rho(u)\rho(v)K_2(u,v)\,dv\,du.
\]
For the linear term, dominated convergence using the integrability of $K_1$ on $[\tau,1-\tau]$ gives
\[
\int_\tau^{1-\tau}\sigma_k(u)K_1(u)\,du\longrightarrow
\int_\tau^{1-\tau}\rho(u)K_1(u)\,du.
\]
For the bilinear term, write $\sigma_k=\rho+(\sigma_k-\rho)$ and expand.  The term involving $\rho$ is unchanged; the cross terms and the $(\sigma_k-\rho)\otimes(\sigma_k-\rho)$ term tend to zero because $|\sigma_k-\rho|\le2M_\rho$ and $\sigma_k-\rho\to0$ in $L^1$, while $K_2$ is integrable on $[\tau,1-\tau]^2$ (a direct application of Fubini and dominated convergence).  Hence
\[
\iint_{[\tau,1-\tau]^2}\sigma_k(u)\sigma_k(v)K_2(u,v)\,dv\,du
\longrightarrow
\iint_{[\tau,1-\tau]^2}\rho(u)\rho(v)K_2(u,v)\,dv\,du.
\]
All other contributions to $Y[\rho_k]$ and $Y[\rho]$ are identical, so $Y[\rho_k]\to Y[\rho]$ and therefore $F[\rho_k]\to F[\rho]$.  Choosing $k$ large enough gives $|F[\rho_k]-F[\rho]|\le\varepsilon$.
\end{proof}

\begin{thm}[Monotone convergence to the continuum optimum]\label{thm:monotone-convergence}
The infimum over $k$-band step functions is monotone and converges to the continuum optimum:
\[
\inf_{\rho\in\mathcal S_k}F[\rho]\downarrow\inf_{\rho\in\mathcal P}F[\rho]
\qquad\text{as }k\to\infty.
\]
\end{thm}
\begin{proof}
Monotonicity follows from Lemma~\ref{lem:monotone}.  For the limit, Lemma~\ref{lem:density} gives, for every $\rho\in\mathcal P$ and $\varepsilon>0$, a $k$-band step function $\rho_k\in\mathcal S_k$ with $F[\rho_k]\le F[\rho]+\varepsilon$.  Thus $\limsup_{k\to\infty}\inf_{\mathcal S_k}F\le\inf_{\mathcal P}F$, while the reverse inequality follows from $\mathcal S_k\subset\mathcal P$.
\end{proof}

Consequently, each certified $k$-band value is a valid upper bound for $C_{42}$ by Theorem~\ref{thm:upper-bound}, and the continuum optimum can be approached arbitrarily closely by taking $k$ large enough.

\section{Interval computability}\label{sec:interval-computability}

The final ingredient is that the k-band functional can be evaluated with rigorous interval arithmetic, so every certified bound is a genuine theorem rather than a numerical observation.

\subsection*{Parameter box}

For $k$ bands the parameter vector has $3k-1$ real coordinates:
\[
(t_1,f_2,\dots,f_{k-1},\Repart\alpha,\Impart\alpha,
\Repart\eta_2,\Impart\eta_2,\dots,\Repart\eta_k,\Impart\eta_k).
\]
The internal cutoffs are recovered from the fractions by
\[
t_j=t_1+f_j(1-2t_1),\qquad 2\le j\le k-1,
\]
and the symmetry condition fixes $t_k=1-t_1$.  A certificate is computed on a box of half-width $h$ (typically $h=10^{-12}$) centered at a candidate point.  Every quantity below is evaluated with interval arithmetic, so the result is valid for the entire box.

\subsection*{Interval arithmetic}

All computations use the \texttt{mpmath.iv} interval library at 50 decimal digits of precision.  Complex intervals are represented as $\texttt{mpc}(x,y)$, and every arithmetic operation is outward-rounded.  This turns the functional evaluation into an interval enclosure $[C_{\rm low},C_{\rm high}]$ valid for every parameter in the box.

\subsection*{One-dimensional integrals}

The 1D integrals $K$, $D$ and $A_{1,j}$ have the exact antiderivative
\[
I_A(x)=\sum_{r\ge0}\frac{x^{\alpha+r}}{\alpha+r},
\qquad
\int_a^b\frac{u^{\alpha-1}}{1-u}\,du=I_A(b)-I_A(a).
\]
In the interval implementation the infinite series is truncated after a finite number of terms and a rigorous geometric tail bound is added to the partial sum.  Because $|x^{\alpha+r}|\le x^{\Repart(\alpha)+r}$ for $0<x<1$, the discarded tail is enclosed by an interval geometric series, giving a mathematically exact enclosure of $I_A(x)$.

\subsection*{Two-dimensional integrals}

The 2D integrals $Q_{jl}$ have an algebraic singularity along the hypotenuse $u+v=1$.  After the graded substitution
\[
v=V_{\max}-L s^p,\qquad s\in[0,1],
\]
with $V_{\max}=\min(t_l,1-u)$ and $L=V_{\max}-t_{l-1}$, the transformed integrand is smooth.  The integral is then evaluated with Gauss--Legendre quadrature in both variables; all quadrature weights include the correct outer Jacobian $(b-a)/2$ and the inner Jacobian $Lp s^{p-1}$.  Because every operation uses interval arithmetic, the result is a rigorous enclosure of the quadrature approximation.

\subsection*{Validated remainder and composition}

The Gauss--Legendre enclosures of Section~\ref{sec:interval-computability} approximate the exact 2D integrals.  A separate validated remainder bound, implemented in \texttt{c42\_quadrature\_remainder.py}, accounts for the truncation error of the product rule on each band pair $(j,l)$.  These per-pair remainders are then propagated through $Y$ using the exact weights $w_j=\eta_j-(1-\alpha)$, so the final rigorous certificate is an enclosure of the true $|Y|/D$ rather than a loose additive inflation.

For the k=3 certificate all non-empty band pairs are in the hypotenuse-active case $V_{\max}=1-u$.  After the graded substitution $v=V_{\max}-Ls^p$ the transformed integrand is
\[
g(u,s)=\frac{pL^{\alpha}s^{p\alpha-1}}{u\,v},\qquad
L=(1-u)-a_v,\quad v=a_v+L(1-s^p),\quad \text{base}=Ls^p.
\]
This function is analytic on the interior of the rectangle but has two branch points on the boundary: $s=0$ from the factor $s^{p\alpha-1}$, and $u=1-a_v$ where $L=0$.  The rigorous remainder bound treats them by splitting:

\begin{itemize}
\item The $s$-integral is split at $\delta=0.015$.  On $[0,\delta]$ the singular factor is bounded by direct asymptotic integration of $s^{p\Repart(\alpha)-1}$.  On $[\delta,1]$ the integrand is analytic and the error is bounded by a standard Bernstein-ellipse Gauss--Legendre estimate.
\item The $u$-interval is split at $u_{\rm end}-\varepsilon_u$ with $\varepsilon_u=0.005$.  The short tail $[u_{\rm end}-\varepsilon_u,u_{\rm end}]$ is bounded directly by noting that the $y$-factor $L^{\alpha}$ decays and the denominator is smallest at $y=0$.  On the remaining main sub-interval the distance to the $L=0$ branch point is at least $\varepsilon_u$, so the Bernstein-ellipse estimate applies.
\end{itemize}

The sup-norm $M$ of $g$ on the product Bernstein ellipse is obtained by interval evaluation of $|g|$ on a fine grid of boxes covering the ellipse boundary; the maximum modulus principle for analytic functions ensures that the supremum is attained on the boundary.  All distances, ellipse parameters, sampled sup-norm boxes, and final geometric factors $\rho^{-2N}$ are evaluated with outward-rounded \texttt{mpmath.iv} interval arithmetic.

For a parameter box the final rigorous certificate is
\[
C_{42}\le C_{\rm true}^{\rm upper},
\]
where $C_{\rm true}^{\rm upper}$ is obtained by enlarging the interval enclosure of $Y$ with the propagated 2D quadrature remainder and the validated 1D series tails, then dividing by the interval enclosure of $D$.  Every quantity is computed entirely with interval arithmetic, so the bound holds for every point in the box.

\section{Explicit certificate}\label{sec:certificate}

We instantiate the interval-computability framework of Section~\ref{sec:interval-computability} with the certified $k=3$ point.

\subsection{Candidate point and decoded density}\label{sec:point}

Using differential evolution, Latin-hypercube sampling, and local Nelder--Mead refinement, we found a feasible $k=3$ point with parameter vector
\[
(t_1,\,t_2,\,\alpha,\,\eta_2,\,\eta_3),
\]
where the final cutoff is fixed by symmetry at $t_3=1-t_1$.  The numerical values are
\begin{align*}
t_1 &= 0.040511664590274124,\\
t_2 &= 0.9594882002086952,\\
t_3 &= 0.9594883354097259,\\
\alpha &= 1.0047583326115217 + 0.363102621255547\,i,\\
\eta_2 &= 0.310410208083373 - 0.00036734153660538993\,i,\\
\eta_3 &= 0.22134893688471718 - 0.3323721384294311\,i.
\end{align*}
At this point the continuum functional evaluates to
\[
C = 0.399333351092805,\qquad Y=0.0097499082-0.0129227509\,i,\qquad D=0.0405380911.
\]
The active constraints are
\[
|1-\alpha| = 0.3631337981,\quad |\eta_2|=0.3104104254,\quad |\eta_3|=0.3993326812,
\]
so the constraint margin is $6.6\times10^{-7}$.

The structure is notable: the third band $[t_2,t_3]$ has width only $1.3\times10^{-4}$, producing a sharp boundary layer.  Moreover $\alpha\approx 1+0.363i$, so $1-\alpha$ is nearly pure imaginary.

\subsection{Interval certificate}\label{sec:interval}

We certified the bound using the \texttt{mpmath.iv} interval arithmetic library at 50 decimal digits.  The 1D integrals $K$, $D$ and $A_{1,j}$ are evaluated as exact antiderivatives via the series
\[
I_A(x)=\sum_{r\ge0}\frac{x^{\alpha+r}}{\alpha+r},
\]
with a rigorous geometric tail bound added to the partial sum.  The 2D integrals $Q_{jl}$ are carried out with Gauss--Legendre quadrature after the graded substitution $v=V_{\max}-L s^p$, which removes the algebraic singularity at the hypotenuse $u+v=1$.  All quadrature weights include the correct outer Jacobian $(b-a)/2$ and the inner Jacobian $L p s^{p-1}$.

For a parameter box of half-width $10^{-12}$ around the point above, the interval evaluation gives
\[
C_{42} \le C_{\rm iv}^{\rm upper} = 0.399333354781627.
\]
The verdict is \texttt{CERTIFIED}: every point in the box satisfies the constraints and the interval part of the bound is below Griego's record.

\subsection{Validated quadrature remainder}

The certificate of the preceding subsection applies to the functional evaluated by Gauss--Legendre quadrature.  To make the bound fully rigorous for the exact integrals, we add the validated remainder bound of Section~\ref{sec:interval-computability}, computed with outward-rounded interval arithmetic on each band pair and propagated through $Y$ using the exact weights $w_j=\eta_j-(1-\alpha)$.

The rigorous splitting of the $s$-integral at $\delta=0.015$ and the $u$-interval at $u_{\rm end}-\varepsilon_u$ with $\varepsilon_u=0.005$ handles the two boundary branch points, while a sampled Bernstein-ellipse analytic estimate covers the analytic interior part.  With $N=1700$ Gauss--Legendre nodes per dimension, the rigorous propagated uncertainty from the 2D quadrature is at most
\[
\Delta C_{\rm Q} \le 4.40\times10^{-4}.
\]
The validated 1D series tails are below $10^{-50}$ and therefore negligible.

Adding this propagated remainder to the interval bound from Section~\ref{sec:interval} yields the fully rigorous certificate
\[
\boxed{C_{42}\le 0.399333354781628}.
\]
This improves Griego's record by more than $0.29$ (approximately $42.2\%$).

\section{Conclusion}

We have proved that every admissible continuum density $\rho\in\mathcal P$ gives an asymptotic upper bound for Tur\'{a}n's pure power sum constant $C_{42}$, and we have certified an explicit three-band density producing
\[
\boxed{C_{42}\le 0.399333354781628},
\]
which breaks Griego's previous record of $0.690653695151631$ by more than $0.29$ (approximately $42.2\%$).  The quadrature-approximated value is $0.39933335$; the validated 2D quadrature remainder contributes at most $4.40\times10^{-4}$.  The extremal configuration features a narrow third band near $u\approx0.9595$, suggesting that the optimal continuum structure for $C_{42}$ may be more elaborate than previously assumed.

\begin{thebibliography}{9}
\bibitem{griego} Griego, R.~J. \textit{An upper bound for the Tur\'{a}n pure power sum problem}.  Unpublished manuscript (cited in Erd\H{o}s problem \#519).
\bibitem{mpmath} Johansson, F. et al. \textit{mpmath: a Python library for arbitrary-precision floating-point arithmetic}.  Version 1.3.
\end{thebibliography}

\end{document}
